Forcing for Isabelle

### 2018-12-28 LICS/intro_m.tex
trabajos relacionados

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%          
\section{Introduction}
% no \IEEEPARstart
Zermelo-Fraenkel Set Theory ($\ZF$) has a prominent place among formal
theories; in particular, it provides a foundation for mathematics and
most of the toolkit used everyday by the computer scientist has also
Set Theory at its base (although much of it can be based in other
formalisms, such as Category Theory) \fbox{citation needed,
  Aczel?}. In this time of mechanization of
mathematics~\cite{avigad2018mechanization}, it seems natural to ask
for a mechanization of the most salient results of Set Theory.
\fbox{Y entra de lleno en la intersección de lógica  y cs}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%          
\section{Introduction}
% no \IEEEPARstart
Zermelo-Fraenkel Set Theory ($\ZF$) has a prominent place among formal
theories; in particular, it provides a foundation for mathematics and
most of the formal toolkit used everyday by the computer scientist has
also Set Theory at its base (cf.~\cite{paulson1995set}). In this time
of mechanization of mathematics~\cite{avigad2018mechanization}, it
seems natural to ask for a mechanization of the most salient results
of Set Theory.

@@

It might be a little surprising the lack of formalizations of forcing
and generic extensions. As far as we know, the development of
\citet{JFR6232} in homotopy type theory for constructing generic
extensions in a sheaf-theoretic setting is the unique mechanization of
forcing. This contrast with the fruitful use of forcing techniques to
extend the Curry-Howard isomorphism to classical axioms
\cite{Miquel:2011:FPT:2058525.2059614,lmcs:1070}. Moreover, the
combination of forcing with intuitionistic type theory
\cite{coquand2010note,coquand2012computational} gives rise to an
algorithm to obtain witnesses of the continuity of definable
functionals.

% moreover forcing translations \cite{jaber:hal-01319066}.
